Mapping mutational effects along the evolutionary landscape of HIV envelope

### 2017-12-10 paper/manuscript.tex
a few more tiny tweaks

But our maps come with a serious caveat: each one is measured for just a single Env variant.
The major question that our study aimed to answer is whether the maps are still useful for evolutionary questions, or whether Env's amino-acid preferences shift so rapidly that each map only applies to the specific HIV strain for which it was measured.
This question is reminiscent of one that was grappled with in the early days of protein crystallography, when it first became possible to build maps of a protein's structure.
Because it was not (and is still not) possible to crystallize every variant of a protein, it was necessary to determine whether protein-structure maps could be usefully generalized among homologs.
Fortunately for the utility of structural biology, it soon became apparent that closely homologous proteins have similar structures~\citep{chothia1986relation,sander1991database}.
This rough generalizability of protein-structure maps holds even for a protein as conformationally complex as Env -- for although there are many examples of mutations that alter Env's structure and dynamics~\citep{kwong2000structures,white2010molecular,almond2010structural,davenport2013isolate}, these alterations are sufficiently modest that a few structural maps have facilitated the interpretation of studies on a vast number of HIV strains.

>>>>

But our maps come with a serious caveat: each one is measured for just a single Env variant.
The major question that our study aimed to answer is whether the maps are still useful for evolutionary questions, or whether Env's amino-acid preferences shift so rapidly that each map only applies to the specific HIV strain for which it was measured.
This question is reminiscent of one that was grappled with in the early days of protein crystallography, when it first became possible to build maps of a protein's structure.
Because it was not (and is still not) possible to crystallize every variant of a protein, it was necessary to determine whether protein structures could be usefully generalized among homologs.
Fortunately for the utility of structural biology, it soon became apparent that closely homologous proteins have similar structures~\citep{chothia1986relation,sander1991database}.
This rough generalizability of protein structures holds even for a protein as conformationally complex as Env -- for although there are many examples of mutations that alter Env's structure and dynamics~\citep{kwong2000structures,white2010molecular,almond2010structural,davenport2013isolate}, these alterations are sufficiently modest that a few structural maps have facilitated the interpretation of studies on a vast number of HIV strains.
